\section{Related Work}

\paragraph{Memory Storage, Admission, and Retrieval.}
Existing architectures focus on memory storage structures, retrieval models, and periodic summarization or compression. Works such as \fname{MemGPT} manage memory via paging and swapping between a context window and external storage \cite{packer_memgpt_2024}. \fname{Mem0} provides CRUD-like operations over natural-language facts \cite{chhikara_mem0_2025}, while systems like \fname{A-MEM} and \fname{MemoryOS} focus on hierarchical organization, node consolidation, and context length reduction \cite{xu_-mem_2025,kang_memory_2025}. More recent methods learn memory operation selection or adaptive structures \cite{yu_agentic_2026,lu_choosing_2026,xu_structmem_2026,zhang_adaptive_2026}. 
Unlike these frameworks which optimize storage allocation or retrieval performance, \bench{} and \method{} focus strictly on \emph{post-admission validity revision}—validating whether existing memory records remain logically active or superseded as new evidence chronologically arrives.

\paragraph{Memory Benchmarks.}
Standard evaluations assess long-term retrieval, QA over extended chat histories, or task success in evolving virtual environments. The \textsc{LoCoMo} benchmarks evaluate conversational memory recall over tens of thousands of tokens \cite{maharana_evaluating_2024,li_locomo-plus_2026}. The \textsc{LongMemEval} family assesses temporal updates and experience acquisition in dialogue systems \cite{wu_longmemeval_2025,wu_longmemeval-v2_2026}. Other benchmarks study memory structure or self-evolving retrieval performance \cite{tan_membench_2025,shutova_evaluating_2026,wang_evomembench_2026,hu_evaluating_2026}. 
In contrast to evaluating memory through downstream answer accuracy (which can mask invalid memory states), \bench{} scores the record-level validity mapping directly, tracking evidence grounding and multi-dimensional error metrics.

\paragraph{Structured Inference and Runtime Enforcement.}
Inference-time scaffolds structure language model reasoning without parameter updates. \fname{ReAct} interleaves reasoning and actions \cite{yao_react_2023}, while \fname{Reflexion} and \fname{Self-Refine} implement feedback loops for self-correction \cite{shinn_reflexion_2023,madaan_self-refine_2023}. Reasoning pathways are generalized into thoughts in \textsc{Tree of Thoughts} and \textsc{Graph of Thoughts} \cite{yao_tree_2023,besta_graph_2024,zhou_language_2024,luo_graph_2026}. Embodied agents like \fname{Voyager} execute neural code proposals within deterministic environment engines \cite{wang_voyager_2023}. 
\method{} builds on these paradigms by splitting opaque neural generation from deterministic, symbolic state updates. However, we apply this separation specifically to memory revision, routing neural proposals through a symbolic Guard to verify references and resolve conflicts.

\paragraph{Benchmark Validity and Metamorphic Testing.}
Evaluating the robustness of benchmark evaluations is critical to prevent metric contamination. Metamorphic testing validates system behavior under semantics-preserving transformations (e.g., identifier renaming, event permutation) to assert mathematical equivariance and identify shortcut-learning patterns in models. We employ these principles to audit our diagnostic channels and verify the correctness of the reference transition engine.
