\section{Analysis and Limitations}

We analyze the theoretical and empirical characteristics of \method{} across three epistemic categories to clearly define its boundaries.

\subsection{System Characteristics and Boundaries}

\paragraph{Guaranteed by Construction.}
Several key safety properties are guaranteed by the structural design of \method{}:
\begin{itemize}[leftmargin=*]
\item \textbf{Complete Mediation and Authorization:} Under the mediated deployment boundary, every persistent-memory write is filtered by $G_\Gamma$; actions outside the legal language are not committed.
\item \textbf{Referential Integrity:} Predicates enforce that target and replacement identifiers must exist in the public view.
\item \textbf{Replayability and Noninterference:} Given a complete certificate, deterministic replay yields the same post-state, and untargeted records are unchanged.
\end{itemize}

\paragraph{Observed Empirically.}
On the L4 evaluation split, we observe the following:
\begin{itemize}[leftmargin=*]
\item \textbf{Accuracy and Mediation Trade-offs:} \method{} improves state reliability and guarantees a schema-valid projected response, but it does not dominate decision or evidence accuracy. A rejected patch is a no-commit outcome, not proof that the pre-existing state is safe.
\item \textbf{Backbone Sensitivity:} Benefits are largest when direct generation fails to express the state contract; stronger native structured-output behavior narrows the gap.
\end{itemize}

\paragraph{Not Guaranteed.}
The system does not guarantee:
\begin{itemize}[leftmargin=*]
\item \textbf{Semantic Truth:} The Guard verifies structural preconditions and evidence grounding, but cannot verify if a proposed fact is historically or semantically true.
\item \textbf{Proposal Completeness:} The module is bounded by the model's generation capacity; if the proposer omits a valid update, the system cannot infer it.
\item \textbf{Universal Transfer:} Performance depends on the frozen backbone's capacity to follow action-proposal formatting.
\end{itemize}

\subsection{Limitations}

Several limitations define the current scope of our work:
\begin{itemize}[leftmargin=*]
\item \textbf{Synthetic Ontology and NL Entailment:} The transition ontology in \bench{} simplifies organic language variability, and incomplete natural-language entailment means the symbolic Guard cannot verify semantic truth.
\item \textbf{Template-Family Generalization:} Evaluation is conducted over template-family strata rather than arbitrary real-world conversational databases, which might limit external validity.
\item \textbf{Perturbation Basis:} The seven controlled operators are an auditable diagnostic basis, not an exhaustive model of organic failures; nonlinear interactions may not be identifiable from the local response matrix.
\item \textbf{Proposal Boundedness:} The runtime cannot recover omitted semantic proposals if the neural model fails to propose them.
\item \textbf{Incomplete Organic Validation:} The present study uses controlled template families. External validity requires deployment traces, naturally occurring corrections, and downstream write-through measurements.
\end{itemize}
Future work should investigate organic traces, online multi-agent revision, and learned proposers whose training objective directly balances semantic recall with authorized commit quality.
