\documentclass[letterpaper]{article}
\usepackage[submission]{aaai2027}
\usepackage[hyphens]{url}
\usepackage{graphicx}
\urlstyle{rm}
\def\UrlFont{\rm}
\usepackage{natbib}
\usepackage{caption}
\frenchspacing

\pdfinfo{
/TemplateVersion (2027.1)
}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{xspace}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric,arrows,positioning,calc,fit}
\newcolumntype{Y}{>{\raggedright\arraybackslash}X}

\newcommand{\method}{MemPatch}
\newcommand{\bench}{MemPatch-Bench}
\newcommand{\rmi}{Rapid Memory Integration}
\newcommand{\rmiabbr}{RMI}
\newcommand{\dpafull}{Revision Guard}
\newcommand{\dpa}{\dpafull{}}
\newcommand{\pathfull}{\method{}}
\newcommand{\pathnodpa}{Typed Revision Scaffold}
\newcommand{\pathdirect}{Direct State Prediction}
\newcommand{\field}[1]{\textit{#1}}
\newcommand{\fname}[1]{{\fontfamily{phv}\selectfont\small #1}}
\newcommand{\state}{\field{memory\_state}}
\newcommand{\decision}{\field{decision}}
\newcommand{\evidence}{\field{evidence\_event\_ids}}
\newcommand{\diagnosis}{\field{failure\_diagnosis}}
\newcommand{\answer}{\field{answer}}
\newcommand{\joint}{joint revision success}

\title{MemPatch: Evidential Revision Scaffolds for Rapid Memory Integration in LLM Agents}
\author{Anonymous Submission}
\affiliations{}

\begin{document}
\maketitle

\begin{abstract}
\input{sections/00_abstract.tex}
\end{abstract}

\input{sections/01_introduction.tex}
\input{sections/02_related_work.tex}
\input{sections/03_problem_formulation.tex}
\input{sections/04_mempatch_bench.tex}
\input{sections/05_method.tex}
\input{sections/06_experiments.tex}
\input{sections/07_analysis_limitations.tex}
\input{sections/08_conclusion.tex}

\begin{thebibliography}{24}
\providecommand{\natexlab}[1]{#1}

\bibitem[{Besta et~al.(2024)Besta, Blach, Kubicek, Gerstenberger, Podstawski,
  Gianinazzi, Gajda, Lehmann, Niewiadomski, Nyczyk, and
  Hoefler}]{besta_graph_2024}
Besta, M.; Blach, N.; Kubicek, A.; Gerstenberger, R.; Podstawski, M.;
  Gianinazzi, L.; Gajda, J.; Lehmann, T.; Niewiadomski, H.; Nyczyk, P.; and
  Hoefler, T. 2024.
\newblock Graph of {Thoughts}: {Solving} {Elaborate} {Problems} with {Large}
  {Language} {Models}.
\newblock \emph{Proceedings of the AAAI Conference on Artificial Intelligence},
  38(16): 17682--17690.
\newblock ArXiv:2308.09687 [cs.CL].

\bibitem[{Chhikara et~al.(2025)Chhikara, Khant, Aryan, Singh, and
  Yadav}]{chhikara_mem0_2025}
Chhikara, P.; Khant, D.; Aryan, S.; Singh, T.; and Yadav, D. 2025.
\newblock Mem0: {Building} {Production}-{Ready} {AI} {Agents} with {Scalable}
  {Long}-{Term} {Memory}.
\newblock ArXiv:2504.19413 [cs.CL].

\bibitem[{Hu, Wang, and McAuley(2026)}]{hu_evaluating_2026}
Hu, Y.; Wang, Y.; and McAuley, J. 2026.
\newblock Evaluating {Memory} in {LLM} {Agents} via {Incremental}
  {Multi}-{Turn} {Interactions}.
\newblock ArXiv:2507.05257 [cs.CL].

\bibitem[{Kang et~al.(2025)Kang, Ji, Zhao, and Bai}]{kang_memory_2025}
Kang, J.; Ji, M.; Zhao, Z.; and Bai, T. 2025.
\newblock Memory {OS} of {AI} {Agent}.
\newblock ArXiv:2506.06326 [cs.AI].

\bibitem[{Li et~al.(2026)Li, Guo, Zhang, Xu, Huang, Liu, Xu, Xu, and
  Liu}]{li_locomo-plus_2026}
Li, Y.; Guo, W.; Zhang, L.; Xu, R.; Huang, M.; Liu, H.; Xu, L.; Xu, Y.; and
  Liu, J. 2026.
\newblock Locomo-{Plus}: {Beyond}-{Factual} {Cognitive} {Memory} {Evaluation}
  {Framework} for {LLM} {Agents}.
\newblock ArXiv:2602.10715 [cs.CL].

\bibitem[{Lu et~al.(2026)Lu, Wu, Liu, Xu, Li, Wang, Hu, Ding, Sun, Lu, and
  Zhang}]{lu_choosing_2026}
Lu, M.; Wu, M.; Liu, F.; Xu, J.; Li, W.; Wang, H.; Hu, Z.; Ding, Y.; Sun, Y.;
  Lu, J.; and Zhang, Y. 2026.
\newblock Choosing {How} to {Remember}: {Adaptive} {Memory} {Structures} for
  {LLM} {Agents}.
\newblock ArXiv:2602.14038 [cs.AI].

\bibitem[{Luo et~al.(2026)Luo, Gao, Teng, Wen, Jiang, Zhang, Sun, Zhang, Feng,
  Liu, Zhang, and Pei}]{luo_graph_2026}
Luo, Y.; Gao, R.; Teng, L.; Wen, X.; Jiang, J.; Zhang, Q.; Sun, Y.; Zhang, S.;
  Feng, J.; Liu, T.; Zhang, W.; and Pei, D. 2026.
\newblock Graph of {States}: {Solving} {Abductive} {Tasks} with {Large}
  {Language} {Models}.
\newblock ArXiv:2603.21250 [cs.AI].

\bibitem[{Madaan et~al.(2023)Madaan, Tandon, Gupta, Hallinan, Gao, Wiegreffe,
  Alon, Dziri, Prabhumoye, Yang, Gupta, Majumder, Hermann, Welleck,
  Yazdanbakhsh, and Clark}]{madaan_self-refine_2023}
Madaan, A.; Tandon, N.; Gupta, P.; Hallinan, S.; Gao, L.; Wiegreffe, S.; Alon,
  U.; Dziri, N.; Prabhumoye, S.; Yang, Y.; Gupta, S.; Majumder, B.~P.; Hermann,
  K.; Welleck, S.; Yazdanbakhsh, A.; and Clark, P. 2023.
\newblock Self-{Refine}: {Iterative} {Refinement} with {Self}-{Feedback}.
\newblock ArXiv:2303.17651 [cs.CL].

\bibitem[{Maharana et~al.(2024)Maharana, Lee, Tulyakov, Bansal, Barbieri, and
  Fang}]{maharana_evaluating_2024}
Maharana, A.; Lee, D.-H.; Tulyakov, S.; Bansal, M.; Barbieri, F.; and Fang, Y.
  2024.
\newblock Evaluating {Very} {Long}-{Term} {Conversational} {Memory} of {LLM}
  {Agents}.
\newblock ArXiv:2402.17753 [cs.CL].

\bibitem[{Packer et~al.(2024)Packer, Wooders, Lin, Fang, Patil, Stoica, and
  Gonzalez}]{packer_memgpt_2024}
Packer, C.; Wooders, S.; Lin, K.; Fang, V.; Patil, S.~G.; Stoica, I.; and
  Gonzalez, J.~E. 2024.
\newblock {MemGPT}: {Towards} {LLMs} as {Operating} {Systems}.
\newblock ArXiv:2310.08560 [cs.AI].

\bibitem[{Shinn et~al.(2023)Shinn, Cassano, Berman, Gopinath, Narasimhan, and
  Yao}]{shinn_reflexion_2023}
Shinn, N.; Cassano, F.; Berman, E.; Gopinath, A.; Narasimhan, K.; and Yao, S.
  2023.
\newblock Reflexion: {Language} {Agents} with {Verbal} {Reinforcement}
  {Learning}.
\newblock ArXiv:2303.11366 [cs.AI].

\bibitem[{Shutova et~al.(2026)Shutova, Olenina, Vinogradov, and
  Sinitsin}]{shutova_evaluating_2026}
Shutova, A.; Olenina, A.; Vinogradov, I.; and Sinitsin, A. 2026.
\newblock Evaluating {Memory} {Structure} in {LLM} {Agents}.
\newblock ArXiv:2602.11243 [cs.LG].

\bibitem[{Tan et~al.(2025)Tan, Zhang, Ma, Chen, Dai, and
  Dong}]{tan_membench_2025}
Tan, H.; Zhang, Z.; Ma, C.; Chen, X.; Dai, Q.; and Dong, Z. 2025.
\newblock {MemBench}: {Towards} {More} {Comprehensive} {Evaluation} on the
  {Memory} of {LLM}-based {Agents}.
\newblock ArXiv:2506.21605 [cs.CL].

\bibitem[{Wang et~al.(2023)Wang, Xie, Jiang, Mandlekar, Xiao, Zhu, Fan, and
  Anandkumar}]{wang_voyager_2023}
Wang, G.; Xie, Y.; Jiang, Y.; Mandlekar, A.; Xiao, C.; Zhu, Y.; Fan, L.; and
  Anandkumar, A. 2023.
\newblock Voyager: {An} {Open}-{Ended} {Embodied} {Agent} with {Large}
  {Language} {Models}.
\newblock ArXiv:2305.16291 [cs.AI].

\bibitem[{Wang et~al.(2026)Wang, Zhang, Chi, Yu, Li, Peng, Tong, Zhang, Zhou,
  and Li}]{wang_evomembench_2026}
Wang, Y.; Zhang, Z.; Chi, M.; Yu, K.; Li, Y.; Peng, M.; Tong, B.; Zhang, C.;
  Zhou, Y.; and Li, J. 2026.
\newblock {EvoMemBench}: {Benchmarking} {Agent} {Memory} from a
  {Self}-{Evolving} {Perspective}.
\newblock ArXiv:2605.18421 [cs.CL].

\bibitem[{Wu et~al.(2026)Wu, Ji, Kawatkar, Kwan, Gu, Peng, and
  Chang}]{wu_longmemeval-v2_2026}
Wu, D.; Ji, Z.; Kawatkar, A.; Kwan, B.; Gu, J.-C.; Peng, N.; and Chang, K.-W.
  2026.
\newblock {LongMemEval}-{V2}: {Evaluating} {Long}-{Term} {Agent} {Memory}
  {Toward} {Experienced} {Colleagues}.
\newblock ArXiv:2605.12493 [cs.CL].

\bibitem[{Wu et~al.(2025)Wu, Wang, Yu, Zhang, Chang, and
  Yu}]{wu_longmemeval_2025}
Wu, D.; Wang, H.; Yu, W.; Zhang, Y.; Chang, K.-W.; and Yu, D. 2025.
\newblock {LongMemEval}: {Benchmarking} {Chat} {Assistants} on {Long}-{Term}
  {Interactive} {Memory}.
\newblock ArXiv:2410.10813 [cs.CL].

\bibitem[{Xu et~al.(2026)Xu, Chen, Fang, Zhong, Yao, Zhu, Du, and
  Deng}]{xu_structmem_2026}
Xu, B.; Chen, Y.; Fang, J.; Zhong, R.; Yao, Y.; Zhu, Y.; Du, L.; and Deng, S.
  2026.
\newblock {StructMem}: {Structured} {Memory} for {Long}-{Horizon} {Behavior} in
  {LLMs}.
\newblock ArXiv:2604.21748 [cs.CL].

\bibitem[{Xu et~al.(2025)Xu, Liang, Mei, Gao, Tan, and Zhang}]{xu_-mem_2025}
Xu, W.; Liang, Z.; Mei, K.; Gao, H.; Tan, J.; and Zhang, Y. 2025.
\newblock A-{MEM}: {Agentic} {Memory} for {LLM} {Agents}.
\newblock ArXiv:2502.12110 [cs.CL].

\bibitem[{Yao et~al.(2023{\natexlab{a}})Yao, Yu, Zhao, Shafran, Griffiths, Cao,
  and Narasimhan}]{yao_tree_2023}
Yao, S.; Yu, D.; Zhao, J.; Shafran, I.; Griffiths, T.~L.; Cao, Y.; and
  Narasimhan, K. 2023{\natexlab{a}}.
\newblock Tree of {Thoughts}: {Deliberate} {Problem} {Solving} with {Large}
  {Language} {Models}.
\newblock ArXiv:2305.10601 [cs.CL].

\bibitem[{Yao et~al.(2023{\natexlab{b}})Yao, Zhao, Yu, Du, Shafran, Narasimhan,
  and Cao}]{yao_react_2023}
Yao, S.; Zhao, J.; Yu, D.; Du, N.; Shafran, I.; Narasimhan, K.; and Cao, Y.
  2023{\natexlab{b}}.
\newblock {ReAct}: {Synergizing} {Reasoning} and {Acting} in {Language}
  {Models}.
\newblock ArXiv:2210.03629 [cs.CL].

\bibitem[{Yu et~al.(2026)Yu, Yao, Xie, Tan, Feng, Li, and Wu}]{yu_agentic_2026}
Yu, Y.; Yao, L.; Xie, Y.; Tan, Q.; Feng, J.; Li, Y.; and Wu, L. 2026.
\newblock Agentic {Memory}: {Learning} {Unified} {Long}-{Term} and
  {Short}-{Term} {Memory} {Management} for {Large} {Language} {Model} {Agents}.
\newblock ArXiv:2601.01885 [cs.CL].

\bibitem[{Zhang et~al.(2026)Zhang, Jiang, Wang, Behr, Zhao, Friedman, Chu, and
  Anoun}]{zhang_adaptive_2026}
Zhang, G.; Jiang, W.; Wang, X.; Behr, A.; Zhao, K.; Friedman, J.; Chu, X.; and
  Anoun, A. 2026.
\newblock Adaptive {Memory} {Admission} {Control} for {LLM} {Agents}.
\newblock ArXiv:2603.04549 [cs.AI].

\bibitem[{Zhou et~al.(2024)Zhou, Yan, Shlapentokh-Rothman, Wang, and
  Wang}]{zhou_language_2024}
Zhou, A.; Yan, K.; Shlapentokh-Rothman, M.; Wang, H.; and Wang, Y.-X. 2024.
\newblock Language {Agent} {Tree} {Search} {Unifies} {Reasoning} {Acting} and
  {Planning} in {Language} {Models}.
\newblock ArXiv:2310.04406 [cs.AI].

\end{thebibliography}


\end{document}
